The pollination trade-off

### 2018-09-19 paper/manuscript.Rmd
Update paper's TODO

* References to the introduction
* Discussion from bullet-points to actual paragraphs. I will do that once we all agree with the quantitative methodology and getting some contributions for the interpretation of the results
* Spell-check everything
* Finish off the supplementary materials
* Write the abstract

>>>>

* References to the introduction
* Discussion from bullet-points to actual paragraphs. I will do that once we all agree with the quantitative methodology and getting some contributions for the interpretation of the results
* Spell-check everything
* Write the abstract
